Market Simulator

### 2020-08-18 analysis/05_market_simulator.Rmd
Working through getting a sliderInput for some Persona Inputs

    beta_persona$p1_value[beta_persona$levels %in% input$p1_national_news == '0'] <- 0
    beta_persona$p1_value[beta_persona$levels == '1'] <- 1
    beta_persona$p1_value[beta_persona$levels == '2'] <- 2
    beta_persona$p1_value[beta_persona$levels == '3'] <- 3
    beta_persona$p1_value[beta_persona$levels == '4'] <- 4
    beta_persona$p1_value[beta_persona$levels == '5'] <- 5
    beta_persona$p1_value[beta_persona$levels == '6'] <- 6
    beta_persona$p1_value[beta_persona$levels == '7'] <- 7

    beta_persona$p1_value[beta_persona$levels %in% input$p1_national_news] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_international_news] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_news_medium] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_follow_gov] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_travel_developing] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_political_pref] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_institution_trust] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_others_charitable] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_worship_attendence] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_religion_importance] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_religion] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_charity_importance] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_trust_in_charity] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_donation_frequency] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_donation_amount] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_volunteer_12] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_volunteer_frequency] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_personal_activism] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_family_activism] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_religious_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_sport_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_art_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_labor_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_political_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_environmental_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_professional_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_humanitarian_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_consumer_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_other_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_gender] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_marital_status] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_education] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_income] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_race] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_age] <- 1

@@

    beta_persona$p2_value[beta_persona$levels == '0'] <- 0
    beta_persona$p2_value[beta_persona$levels == '1'] <- 1
    beta_persona$p2_value[beta_persona$levels == '2'] <- 2
    beta_persona$p2_value[beta_persona$levels == '3'] <- 3
    beta_persona$p2_value[beta_persona$levels == '4'] <- 4
    beta_persona$p2_value[beta_persona$levels == '5'] <- 5
    beta_persona$p2_value[beta_persona$levels == '6'] <- 6
    beta_persona$p2_value[beta_persona$levels == '7'] <- 7

@@

    beta_persona$p3_value[beta_persona$levels %in% input$p3_national_news] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_international_news] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_news_medium] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_follow_gov] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_travel_developing] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_political_pref] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_institution_trust] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_others_charitable] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_worship_attendence] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_religion_importance] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_religion] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_charity_importance] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_trust_in_charity] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_donation_frequency] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_donation_amount] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_volunteer_12] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_volunteer_frequency] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_personal_activism] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_family_activism] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_religious_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_sport_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_art_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_labor_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_political_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_environmental_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_professional_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_humanitarian_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_consumer_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_other_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_gender] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_marital_status] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_education] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_income] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_race] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_age] <- 1
    beta_persona

})
```

@@

@@

>>>>

    # beta_persona$p1_value[beta_persona$levels %in% input == '0'] <- 0
    # beta_persona$p1_value[beta_persona$levels %in% input == '1'] <- 1
    # beta_persona$p1_value[beta_persona$levels %in% input == '2'] <- 2
    # beta_persona$p1_value[beta_persona$levels %in% input == '3'] <- 3
    # beta_persona$p1_value[beta_persona$levels %in% input == '4'] <- 4
    # beta_persona$p1_value[beta_persona$levels %in% input == '5'] <- 5
    # beta_persona$p1_value[beta_persona$levels %in% input == '6'] <- 6
    # beta_persona$p1_value[beta_persona$levels %in% input == '7'] <- 7

    beta_persona$p1_value[beta_persona$levels %in% input$p1_national_news] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_international_news] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_news_medium] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_follow_gov] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_travel_developing] <- 1

    beta_persona$p1_value[beta_persona$levels == "Political Preference"] = p1_pol_pref()

    beta_persona$p1_value[beta_persona$levels %in% input$p1_institution_trust] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_others_charitable] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_worship_attendence] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_religion_importance] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_religion] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_charity_importance] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_trust_in_charity] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_donation_frequency] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_donation_amount] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_volunteer_12] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_volunteer_frequency] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_personal_activism] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_family_activism] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_religious_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_sport_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_art_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_labor_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_political_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_environmental_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_professional_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_humanitarian_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_consumer_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_other_member] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_gender] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_marital_status] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_education] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_income] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_race] <- 1
    beta_persona$p1_value[beta_persona$levels %in% input$p1_age] <- 1

@@

    # beta_persona$p2_value[beta_persona$levels == '0'] <- 0
    # beta_persona$p2_value[beta_persona$levels == '1'] <- 1
    # beta_persona$p2_value[beta_persona$levels == '2'] <- 2
    # beta_persona$p2_value[beta_persona$levels == '3'] <- 3
    # beta_persona$p2_value[beta_persona$levels == '4'] <- 4
    # beta_persona$p2_value[beta_persona$levels == '5'] <- 5
    # beta_persona$p2_value[beta_persona$levels == '6'] <- 6
    # beta_persona$p2_value[beta_persona$levels == '7'] <- 7

@@

    beta_persona$p3_value[beta_persona$levels %in% input$p3_national_news] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_international_news] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_news_medium] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_follow_gov] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_travel_developing] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_political_pref] <- 1
    # 
    # beta_persona$p3_value[beta_persona$levels == "Political Preference"] <- input$p3_political_pref

    beta_persona$p3_value[beta_persona$levels %in% input$p3_institution_trust] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_others_charitable] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_worship_attendence] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_religion_importance] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_religion] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_charity_importance] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_trust_in_charity] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_donation_frequency] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_donation_amount] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_volunteer_12] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_volunteer_frequency] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_personal_activism] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_family_activism] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_religious_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_sport_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_art_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_labor_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_political_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_environmental_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_professional_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_humanitarian_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_consumer_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_other_member] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_gender] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_marital_status] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_education] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_income] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_race] <- 1
    beta_persona$p3_value[beta_persona$levels %in% input$p3_age] <- 1
    beta_persona

# reactive slider input ----

p1_pol_pref <- reactive({
  input$p1_political_pref
})
```

@@

df <- as.data.frame(matrix(rep(0), nrow = 1))

df$levels = "Rating"

df$p1[df$levels == "Rating"] = p1_pol_pref()

p1_pol_pref <- reactive({
  input$p1_political_pref
})

@@

sliderInput("p1_political_pref",
       label = "Political views from liberal to conservative:",
       min = 0,
       max = 7,
       value = 0)
